Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
yny4

\begin{enumerate}
\item{change 1}
\item{change 2}
\end{enumerate}

@@

\noindent
{\bf Response:}: We thank the referee for this question. The referee is indeed correct that in a 2D system the system remains constant in the $z$ direction. A two-dimensional vesicle membrane is a tube that is infinitely long in the $z$ direction.
On this infinitely long tube (constant in $z$), the line tension is the total tangential force along the circumferential surface. Divide this line tension by the length of the tube would give us the membrane tension (force per unit length) in the $x-y$ plane.  
%
%Consequently it is customary to focus on the 2D system on a plane, and the membrane tension is the membrane force per unit length (the length in the $z$ direction). This means that, after the division by the length in the third ($z$) direction, the membrane tension in the plane is force per length.

@@

\noindent
{\bf Location:} Second paragraph in the new Introduction in page 2.

>>>>

\begin{enumerate}
\item{Second paragraph in page 2, ``....giving rise to membrane rupture and leakage of macromolecules...".}

\item{Second to last paragraph in page 4, ``....suitable for a vesicle in a quiescent flow,"}

\item{New Figure 5(a).}

\item{New Figures 7.}

\item{New \S IV D.}

\item{New Figures 9.}

\item{New Figures 11, and the paragraph above the new Figures 11 in page 17.}

\item{New Figures 13, and the paragraph above the new Figures 13 in page 19.}

\item{Second to last paragraph in page 21.}

\item{Last paragraph in the Discussion session.}

@@

\noindent
{\bf Response:}: We thank the referee for this question. The referee is indeed correct that in a 2D system the system remains constant in the $z$ direction. A two-dimensional vesicle membrane is a tube that is infinitely long in the $z$ direction.
On this infinitely long tube (of which the cross section is independent of $z$), the line tension is the total tangential force along the circumferential surface. Divide this line tension by the length of the tube would give us the membrane tension (force per unit length) in the $x-y$ plane.  
%
%Consequently it is customary to focus on the 2D system on a plane, and the membrane tension is the membrane force per unit length (the length in the $z$ direction). This means that, after the division by the length in the third ($z$) direction, the membrane tension in the plane is force per length.

@@

\noindent
{\bf Location:} Last paragraph in the Discussion session.

### 2021-05-20 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny4

To answer these
questions, we focus on the balance between hydrodynamics stresses,
tension, and elastic stress of a semipermeable membrane under various
flowing conditions and confinement (Figure~\ref{fig:sketch}).
%
Using numerical simulations described in \S~\ref{sec:formulation} and
\S~\ref{sec:numerics} we quantify the effects of water permeability on
the hydrodynamics of a vesicle under mechanical stresses.  Without an
osmotic gradient, we first show that a freely suspended semipermeable
vesicle behaves differently from an impermeable vesicle over a long time
in \S~\ref{sec:free_space}. Next in \S~\ref{sec:confinement} we show
that
%, at normal physiological conditions,
the permeating water flow can be amplified by extreme confinement to give rise to observable change in both  vesicle hydrodynamics and vesicle's water content. 
These results provide insight into quantifying the effects of membrane permeability on vesicle hydrodynamics in microfluidics.
%
%shed light on the dynamic aging process of
%living cells that constantly go through flows and constrictions over a
%period of days.

@@

>>>>

To answer these
questions, we focus on the balance between hydrodynamics stresses,
tension, and elastic stress of a semipermeable membrane under various
flowing conditions and confinement (Figure~\ref{fig:sketch}).
%
Using numerical simulations described in \S~\ref{sec:formulation} and
\S~\ref{sec:numerics} we quantify the effects of water permeability on
the hydrodynamics of a vesicle under mechanical stresses.  Without an
osmotic gradient, we first show that a freely suspended semipermeable
vesicle behaves differently from an impermeable vesicle over a long time
in \S~\ref{sec:free_space}. Next in \S~\ref{sec:confinement} we show
that
%, at normal physiological conditions,
the permeating water flow can be amplified by extreme confinement to give rise to observable change in both  vesicle hydrodynamics and vesicle's water content. 
These results provide insight into quantifying the effects of membrane permeability on vesicle hydrodynamics in microfluidics.
%\textcolor{magenta}{In the literature studies of
%two-dimensional vesicle hydrodynamics revealed salient features that are also observed in three-dimensions, such as a vesicle in shear flow \cite{GhigliottiBibenMisbah2020_JFM,AgarwalBiros2020_PRF}. Even though quantitative connection to  experimental observation requires some adjustment, results from simulating two-dimensional vesicle hydrodynamics can be insightful for the full three-dimensional simulations of a semipermeable vesicle that we are currently undertaking.
%}
%
%shed light on the dynamic aging process of
%living cells that constantly go through flows and constrictions over a
%period of days.

@@

\textcolor{magenta}{In the literature studies of
two-dimensional vesicle hydrodynamics revealed salient features that are also observed in three-dimensions, such as a vesicle in shear flow \cite{GhigliottiBibenMisbah2010_JFM,AgarwalBiros2020_PRF}. Even though quantitative connection to  experimental observation requires some adjustment, results from simulating two-dimensional vesicle hydrodynamics can be insightful for the full three-dimensional simulations of a semipermeable vesicle that we are currently undertaking.
}
